Forecasting the 2024 U.S. Presidential Election Using a Model-Based Approach

### 2024-11-03 paper/paper.qmd
Update paper.qmd

This section examines the relationship between national polling trends,
pollster effects, population demographics, and other factors with
respect to the predicted support levels for Kamala Harris and Donald
Trump in the 2024 U.S. Presidential Election. Using a dataset comprising
polling data from various states and organizations, we applied both
unweighted and weighted linear regression models to identify the key
predictors influencing each candidate's support. Below, we present the
results of our models along with their implications.

>>>>

This section examines the relationship between national polling trends,
pollster effects, population(respondent group), and other factors with
respect to the predicted support levels for Kamala Harris and Donald
Trump in the 2024 U.S. Presidential Election. Using a dataset comprising
polling data from various states and organizations, we applied both
unweighted and weighted linear regression models to identify the key
predictors influencing each candidate's support. Below, we present the
results of our models along with their implications.
